% =====================================================================
%  Curriculum Vitae — Christopher D. R. Wyatt
%  Self-contained LaTeX source. Builds to cv.pdf.
%  Local build:   latexmk -pdf cv.tex   (or: pdflatex cv.tex)
%  CI build:      see .github/workflows/build.yml
% =====================================================================
\documentclass[11pt,a4paper]{article}

% ---- Packages -------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.2cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{microtype}

% ---- Style ----------------------------------------------------------
\definecolor{accent}{HTML}{2c3e50}

% Section headings: small caps, accent colour, with a rule underneath.
\titleformat{\section}
  {\Large\bfseries\scshape\color{accent}}
  {}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing*{\section}{0pt}{14pt}{8pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\pagestyle{empty}

% ---- Helper: one career/education entry -----------------------------
% \cventry{Role / title}{Institution, location}{Dates}{Description}
\newcommand{\cventry}[4]{%
  \textbf{#1}\par
  \textit{#2}\hfill\textit{#3}\par
  \vspace{2pt}#4\par\vspace{8pt}%
}

% =====================================================================
\begin{document}

% ---- Header ---------------------------------------------------------
\begin{center}
  {\LARGE\bfseries\color{accent} Christopher Douglas Robert Wyatt}\par
  \vspace{4pt}
  {\large Curriculum Vitae}\par
  \vspace{6pt}
  \href{mailto:cw13722@gmail.com}{cw13722@gmail.com}
  \quad$\cdot$\quad Nationality: British\par
  \vspace{4pt}
  \href{https://orcid.org/0000-0001-8033-2213}{ORCID}
  \quad$\cdot$\quad
  \href{https://www.researchgate.net/profile/Christopher-Wyatt-5}{ResearchGate}
  \quad$\cdot$\quad
  \href{https://www.linkedin.com/in/christopher-wyatt-653800235}{LinkedIn}
  \quad$\cdot$\quad
  \href{https://github.com/chriswyatt1}{GitHub}
\end{center}

% ---- Profile --------------------------------------------------------
\section{Profile}

I started my scientific career studying phylogenetics and molecular
evolution, which got me hooked on understanding how the complexity of
life evolved. With the arrival of improved DNA/RNA sequencing
technologies, this opened up a world of high quality empirical data to
better understand molecular regulation and evolution.

I have had the privilege to work with most of these next-generation
sequencing technologies (RNA-Seq, MS-Proteomics, Hi-C) to address key
questions in the field of evolutionary and developmental biology. I am
proficient in Unix, Perl and R, and have working experience with
Python/Matlab. I am also proficient in writing higher-level workflows
using Nextflow, which allows the sharing of reproducible, concise and
scalable pipelines. I have presented my work at many major meetings
across Europe and am confident communicating my ideas and science.

I completed my doctoral training at the Centre for Genomic Regulation
(CRG, Barcelona), where I worked on alternative splicing regulation in
the lab of Manuel Irimia and additionally collaborated with the labs of
Peter Holland (Oxford), Nacho Maeso (CABD, Sevilla) and Bill Keyes
(IGBMC, Strasbourg), working in the fields of transcriptional
regulation, reprogramming, senescence and splicing regulation,
producing a number of high impact publications and gaining a broad
knowledge of many bioscience fields.

Since my PhD, I have worked at UCL (lab of Seirian Sumner) on several
projects, including the use of machine learning to discover genes that
are required for caste identification across wasps. More recently I have
worked for Seqera Labs (the authors of Nextflow) to process biomedical
data for specific startups, which has given me great experience in
producing high quality informatics pipelines for clients.

% ---- Career ---------------------------------------------------------
\section{Education \& Research Career}

\cventry{Pipeline Developer}{Seqera Labs, Barcelona}{June 2021 -- Sept 2021}{%
Writing Nextflow pipelines for several startups as well as documenting
the training material for Nextflow. This gave me in-depth knowledge of
this domain specific language for pipeline development.}

\cventry{Post-doctorate in Evolutionary Genomics / Transcriptomics}{Centre for Biodiversity and Environment Research, UCL, London}{April 2019 -- Feb 2021}{%
Worked on a variety of research projects in the Eusocial Insect Research
Group (Seirian Sumner) using machine learning, transcriptomics and
proteomics approaches (using Nextflow) to explore wasp caste identity
and evolution. Work submitted to bioRxiv prior to publication.}

\cventry{PhD in Biomedicine}{Systems Biology, Centre for Genomic Regulation, Barcelona}{Sept 2015 -- March 2019}{%
Studied the regulation and patterns of alternative splicing during
pre-implantation mammalian development.}

% ---- Projects -------------------------------------------------------
\section{Selected Projects}

\cventry{Eco-Flow --- open-source Nextflow pipelines for agri-ecology}{%
\href{https://eco-flow.github.io/}{eco-flow.github.io} \, $\cdot$ \, \href{https://github.com/eco-flow}{github.com/eco-flow}}{UCL, ongoing}{%
Contributing to a BBSRC-funded community building reproducible,
nf-core-standard Nextflow pipelines that close ``the omics gap in
ecology'', alongside nf-test testing, researcher training, and community
events.}

% ---- Skills ---------------------------------------------------------
\section{Technical Skills}

\textbf{Languages \& tools:} Unix/Bash, Perl, R, Python, Matlab\par
\textbf{Workflows:} Nextflow (nf-core), reproducible \& FAIR pipelines\par
\textbf{Data types:} RNA-Seq, MS-Proteomics, Hi-C, genome assembly\par

% ---- Publications ---------------------------------------------------
% Author name in bold. List maintained from ORCID (0000-0001-8033-2213).
\section{Publications}

\begin{enumerate}[leftmargin=1.4em,labelsep=0.5em,itemsep=5pt,topsep=4pt,label=\arabic*.]
  \item T.D. Doyle, E. Jimenez-Guri, J.C. Barnes, C. Hannah, S. Murray, \textbf{C.D.R. Wyatt}, O.M. Poole \& K.R. Wotton (2025). Long-range pollen transport across the North Sea: Insights from migratory hoverflies landing on a remote oil rig. \textit{Journal of Animal Ecology}, 94(11), 2267-2281. \href{https://doi.org/10.1111/1365-2656.70126}{doi:10.1111/1365-2656.70126}
  \item D. Sampaio Gonçalves, L. Dulac, B. Ritschka, M. Rhinn, A. Klein, \textbf{C.D.R. Wyatt}, M. Irimia \& W.M. Keyes (2025). Senescent cells exhibit features of developmental signaling centres. \textit{bioRxiv} (preprint). \href{https://doi.org/10.1101/2025.10.30.685565}{doi:10.1101/2025.10.30.685565}
  \item A. Di Matteo, E. Belloni, D. Pradella, A.M. Chiaravalli, G.M. Pini, M. Bugatti, R. Alfieri, C. Barzan, E. Franganillo Tena, S. Bione, E. Terenzani, F. Sessa, \textbf{C.D.R. Wyatt} et al. (2023). Alternative Splicing Changes Promoted by NOVA2 Upregulation in Endothelial Cells and Relevance for Gastric Cancer. \textit{International Journal of Molecular Sciences}, 24(9), 8102. \href{https://doi.org/10.3390/ijms24098102}{doi:10.3390/ijms24098102}
  \item \textbf{C.D.R. Wyatt}, M.A. Bentley, D. Taylor, E. Favreau, R.E. Brock, B.A. Taylor, E. Bell, E. Leadbeater \& S. Sumner (2023). Social complexity, life-history and lineage influence the molecular basis of castes in vespid wasps. \textit{Nature Communications}, 14(1). \href{https://doi.org/10.1038/s41467-023-36456-6}{doi:10.1038/s41467-023-36456-6}
  \item \textbf{C.D.R. Wyatt}, B. Pernaute, A. Gohr, M. Miret-Cuesta, L. Goyeneche, Q. Rovira, M.C. Salzer, E. Boke, O. Bogdanovic, S. Bonnal et al. (2022). A developmentally programmed splicing failure contributes to DNA damage response attenuation during mammalian zygotic genome activation. \textit{Science Advances}, 8(15). \href{https://doi.org/10.1126/sciadv.abn4935}{doi:10.1126/sciadv.abn4935}
  \item \textbf{C.D.R. Wyatt}, M. Bentley, D. Taylor, R.E. Brock, B.A. Taylor, E. Bell, E. Leadbeater \& S. Sumner (2020). Genetic toolkit for sociality predicts castes across the spectrum of social complexity in wasps. \textit{bioRxiv} (preprint). \href{https://doi.org/10.1101/2020.12.08.407056}{doi:10.1101/2020.12.08.407056}
  \item E. Belloni, A. Di Matteo, D. Pradella, M. Vacca, \textbf{C.D.R. Wyatt}, R. Alfieri, A. Maffia, S. Sabbioneda \& C. Ghigna (2019). Gene Expression Profiles Controlled by the Alternative Splicing Factor Nova2 in Endothelial Cells. \textit{Cells}, 8(12), 1498. \href{https://doi.org/10.3390/cells8121498}{doi:10.3390/cells8121498}
  \item R.J. Southon, E.F. Bell, P. Graystock, \textbf{C.D.R. Wyatt}, A.N. Radford \& S. Sumner (2019). High indirect fitness benefits for helpers across the nesting cycle in the tropical paper wasp \textit{Polistes canadensis}. \textit{Molecular Ecology}, 28(13), 3271-3284. \href{https://doi.org/10.1111/mec.15137}{doi:10.1111/mec.15137}
  \item F. Marlétaz, P.N. Firbas, I. Maeso, J.J. Tena, O. Bogdanovic, M. Perry, \textbf{C.D.R. Wyatt}, E. de la Calle-Mustienes, S. Bertrand, D. Burguera et al. (2018). Amphioxus functional genomics and the origins of vertebrate gene regulation. \textit{Nature}, 564(7734), 64-70. \href{https://doi.org/10.1038/s41586-018-0734-6}{doi:10.1038/s41586-018-0734-6}
  \item P. Kennedy, G. Baron, B. Qiu, D. Freitak, H. Helanterä, E.R. Hunt, F. Manfredini, T. O'Shea-Wheller, S. Patalano, C.D. Pull, T. Sasaki, D. Taylor, \textbf{C.D.R. Wyatt} et al. (2017). Deconstructing Superorganisms and Societies to Address Big Questions in Biology. \textit{Trends in Ecology \& Evolution}, 32(11), 861-872. \href{https://doi.org/10.1016/j.tree.2017.08.004}{doi:10.1016/j.tree.2017.08.004}
  \item I. Maeso, T.L. Dunwell, \textbf{C.D.R. Wyatt}, F. Marlétaz, B. Vető, J.A. Bernal, S. Quah, M. Irimia \& P.W.H. Holland (2016). Evolutionary origin and functional divergence of totipotent cell homeobox genes in eutherian mammals. \textit{BMC Biology}, 14(1). \href{https://doi.org/10.1186/s12915-016-0267-0}{doi:10.1186/s12915-016-0267-0}
  \item M. Guillemin, L. Contreras-Porcia, M.E. Ramírez, E.C. Macaya, C.B. Contador, H. Woods, \textbf{C. Wyatt} \& J. Brodie (2016). The bladed Bangiales (Rhodophyta) of the South Eastern Pacific: Molecular species delimitation reveals extensive diversity. \textit{Molecular Phylogenetics and Evolution}, 94, 814-826. \href{https://doi.org/10.1016/j.ympev.2015.09.027}{doi:10.1016/j.ympev.2015.09.027}
  \item S. Patalano, A. Vlasova, \textbf{C. Wyatt}, P. Ewels, F. Camara, P.G. Ferreira, C.L. Asher, T.P. Jurkowski, A. Segonds-Pichon, M. Bachman et al. (2015). Molecular signatures of plastic phenotypes in two eusocial insect species with simple societies. \textit{Proceedings of the National Academy of Sciences}, 112(45), 13970-13975. \href{https://doi.org/10.1073/pnas.1515937112}{doi:10.1073/pnas.1515937112}
  \item C. Giampietro, G. Deflorian, S. Gallo, A. Di Matteo, D. Pradella, S. Bonomi, E. Belloni, D. Nyqvist, V. Quaranta, S. Confalonieri, G. Bertalot, F. Orsenigo, F. Pisati, E. Ferrero, G. Biamonti, E. Fredrickx, C. Taveggia, \textbf{C.D.R. Wyatt} et al. (2015). The alternative splicing factor Nova2 regulates vascular development and lumen formation. \textit{Nature Communications}, 6(1). \href{https://doi.org/10.1038/ncomms9479}{doi:10.1038/ncomms9479}
\end{enumerate}

\end{document}
